Bees need larger brains to thrive in urban environments

### 2023-09-08 Manuscript/Ms.Rmd
Data availability statement update

#Load final dataset 
raw = read_csv("../Raw_data/all_cleaning.csv")

@@

All occurrence data used in this study can be downloaded from <https://doi.org/10.15468/dl.5s5kuf>. In addition, bee trait data and code can be found in the online repositories of Zenodo <https://doi.org/10.5281/zenodo.8049996> and Github <https://github.com/ibartomeus/declines_brain.git>.

>>>>

#Load final dataset 
raw = read_csv("../Data/Processing/all_cleaning.csv")

@@

All data and code can be accessed at Dryad Digital Repository: <https://doi.org/10.5061/dryad.zw3r228dr> [@Lanuza2023].
